A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-11-10 response.tex

\textit{I appreciate the authors' efforts in improving the paper, and most of my concerns have been addressed.}

\subsection{Reorganizing related work}

\textit{\textbf{R1:} I have observed that the related work now includes several subsections focusing on APR and patch correctness prediction. It would be beneficial to reorganize and consolidate these subsections into a single coherent section. Furthermore, the section on related work should encompass studies related to bug classification in programming languages with a longer history.}

\vspace*{1em} \noindent \textbf{Response:} Included two research studies in the list of related works. The first is a 1975 study conducted by Enders et al. \cite{endres1975analysis}, which examines common error patterns in the DOS/VS operating system. The second is a study by Flanagan et al. \cite{flanagan1998new}, where they introduce a static debugger for Scheme, a Lisp dialect, centered around the error-prone operators in the language. \todo{How should we consolidate those subsections?}

@@

\subsection{More discussion on the impact of the evolving Rust specification}

\textit{\textbf{R1:} Additionally, I would appreciate it if the authors could discuss the potential impact of the evolving Rust specification. Given that Rust is a novel programming language, it is subject to rapid grammatical changes, which in turn could influence bug characteristics and symptoms.}

\vspace*{1em} \noindent \textbf{Response:} A brief discussion added to the threats to external validity list.

### 2023-11-10 related.tex
added cites for the previous commit

The main intuition in pattern-based program repair methods is that bug fixes follow certain patterns. Thus, having a collection of common bug fix patterns is a crucial step for developing such repair tools. Studying bug fix patterns can be traced back to 1975 when Enders et al introduced a classification of bugs that occur in DOS/VS operating system. This work contends that categorizing bug patterns can aid in uncovering error causes, fixing them, and preventing their recurrence. Flanagan et al. proposed MrSpidey, an interactive static debugger for Scheme (a dialect of Lisp). MrSpidey allows the programmer to browse program invariants and their derivations over error prone patterns (unsafe operators). The user can determine whether the error will actually occur, or if obtaining the correctness proof is unattainable due to the tool's limitations.

>>>>

The main intuition in pattern-based program repair methods is that bug fixes follow certain patterns. Thus, having a collection of common bug fix patterns is a crucial step for developing such repair tools. Studying bug fix patterns can be traced back to 1975 when~\cite{endres1975analysis} introduced a classification of bugs that occur in DOS/VS operating system. This work contends that categorizing bug patterns can aid in uncovering error causes, fixing them, and preventing their recurrence. \cite{flanagan1998new} proposed MrSpidey, an interactive static debugger for Scheme (a dialect of Lisp). MrSpidey allows the programmer to browse program invariants and their derivations over error prone patterns (unsafe operators). The user can determine whether the error will actually occur, or if obtaining the correctness proof is unattainable due to the tool's limitations.
